\begin{center}
\small
\begin{longtable}{p{.1\textwidth}|p{.2\textwidth}|p{.6\textwidth}}
\hline
\textbf{Test \#} & \textbf{Use Case}            & \textbf{Acceptance Criteria} \\ \hline
1                & Retrieve Camera Images       &  \begin{itemize}
												  	\item Can retrieve images from the camera.
												  	\item Provides images in a useful format.
												  \end{itemize}             \\ \hline
2                & Manipulate Image             &  \begin{itemize}
												  	\item Can manipulate images that are taken from the camera.
												  	\item Can manipulate images with a transformation.
												  	\item Can manipulate images with a filter.
												  \end{itemize}                             \\ \hline
3                & Change Stereo Algorithm      &  \begin{itemize}
												  	\item Can select which method of stereo correspondence to use.
												  \end{itemize}                             \\ \hline
4                & Change Stereo Parameters     &  \begin{itemize}
												  	\item Can change the parameters for a particular stereo correspondence algorithm.
												  \end{itemize}                             \\ \hline
5                & Change Classifier Type       &  \begin{itemize}
												  	\item Can change types of classifier used.
												  \end{itemize}                             \\ \hline
6                & Change Classifier Parameters &  \begin{itemize}
												  	\item Can change the parameters on a particular classifier.
												  \end{itemize}                            \\ \hline
7                & Reset Training Data          &  \begin{itemize}
												  	\item Any previous training data can be removed.
												  \end{itemize}                            \\ \hline
8                & View Current Classifications &  \begin{itemize}
												  	\item Existing trained classification labels can be viewed.
												  \end{itemize}                            \\ \hline
9                & Train Classifier             &  \begin{itemize}
												  	\item The classifier can be trained on a new set of classification data.
												  	\item Classification data can be collected at run time with the leap motion, prior to training.
												  \end{itemize}                            \\ \hline
10               & Classify Object              &  \begin{itemize}
													\item The framework can segment an object within an image.
												  	\item The framework will provide a classification label when provided with data to classify.
												  \end{itemize}                            \\ \hline
\caption{Acceptance Criteria \protect {\label{tab:acc_criteria}}}
\end{longtable}

\end{center}